\section{Modeling the voltage pulse generator and the probe}
In this section, I describe the various steps I went through to properly model the voltage pulse generator and the problem it arises.
In the first place, I present a very simple and naive way of modeling the generator, using an ideal voltage source.
Then, after having analyzed the shortcomings of such model, I introduce a better model which better suits an actual generator.
Eventually, I analyze preliminary validation results including the new generator model.

    \subsection{Various generator architectures \ddcnew}
    There are several existing types of pulse generator.
    Some of them are designed as voltage sources, while others are current sources.
    In addition to this, the way their output stage is designed is also the origin of important behavioral differences.
    It is then important to take a quick look at these architectural differences.
%    Because there are various generator architecture, whether they are voltage sources, current sources, or how their output stage is designed, it is important to first take a look at them.
    We can distinguish pulse generator into two categories depending on their output stage coupling: DC-coupled and AC-coupled.
    In my work, I use a voltage source DC-coupled generator, but it is not the case of all other works.
    Therefore, I am going to cite various documented generators which have been used for the study of \bbi.

    For instance, in \cite{japbbi} and \cite{japbbi2}, the authors used an \esd gun to create the pulses on their IC substrate.
    These devices typically have a DC-coupled output, commonly feature an RCR output filter, and are designed to generate single pulses, very short and of very high voltage, without having a fine control over rise and fall times or pulse width.
    Their output impedance is not finely controller when compared to high precision high voltage pulse generators.
    Therefore, it is important to consider these parameters when elaborating an electrical model.

    On the other hand, there are other works, such as \cite{bbiColin}, in which the generator output stage consists in a transformer.
    Therefore, it is AC-coupled to the IC, which changes drastically the electrical behavior of such generator compared to a DC-coupled one.
    For instance, it is not possible to inject energy into the IC outside of pulse edges, while on DC-coupled generators it is.

    Eventually, like in my work, there are very high voltage high precision generators, which are DC-coupled and allow for precise pulse width and voltage set point.
    Their output stage may vary unit to unit, but their output impedance is precisely controller.
    In my case, the generator is specified to deliver its specifications into a \fiftyOhms{50} load.

    With this in mind, let us jump into the next section.

    \subsection{Voltage pulse generator naive model \ddcpu}
    First, let us consider a very simple voltage generator, an ideal variable voltage source, and a very simple probe, a perfect wire.
    In that scenario, as the generator is DC-coupled, it is biasing the substrate at 0 V at rest.
    However, under normal conditions, an IC substrate should not be biased externally.
    Indeed, whether in my model or in an actual IC, it can create unexpected behavior.
    In addition to this, our AVTECH generator does not bias the IC at rest, even when the probe is connected.
    Instead, it is operating in a high-impedance mode where its output presents a very high impedance to the IC backside, thus preventing any undesirable biasing.

    \subsection{More elaborated generator model \ddcnew}
%    \input{3_modeling/figures/genModel}
    In this context, I decided to mimic our actual generator structure in my model to properly appreciate its behavior in the simulations.

    To do so, I chose to use a time-controlled resistor, which is a component available in SPICE.
    It is very straightforward, and consists in dynamically defining the resistor value.
    To that end, before the pulse, its value is high-impedance (100 G\textOmega), during the pulse it is close to zero, and after the pulse it goes back to a high-impedance value.
    By doing so, I am avoiding any bias which could cause unexpected behavior of the model, which then could invalidate the simulation conclusions.

\section{Modeling BBI disturbances: further model validation}
With correct \scs and generator models, it is now possible to simulate \bbi disturbances.
To that end, we distinguish \dwF and \twF substrates, to better analyze their differences, both in behavior and in structure.
As for the previous section, the ICs have the following measurements: a width of $550 \; \mu m$, a depth of $450 \; \mu m$, and a substrate thickness of $140 \; \mu m$, representing 1620 \scs connected to each other in a mesh array.
There are two external power supply rails located at the top and at the bottom of each IC.
The probe is a 30 µm square probe, placed at the IC center, and the generator settings are the following:
\begin{itemize}
    \setlength\itemsep{-0.1em}
    \item Voltage pulse maximum amplitude: -300 V;
    \item Voltage pulse width: 20 ns;
    \item Rise and fall times: 8 ns;
    \item Approximate impedance matching realized thanks to a \fiftyOhms{50} load, as described in the Chapter \ref{chap:2_goodPractices}.
\end{itemize}
For each considered IC, we observe various signals in a two-dimensional view to fully appreciate the spatial behavior of the ICs under \bbi, at the apex of the disturbance:
\begin{itemize}
    \setlength\itemsep{-0.1em}
    \item The power supply voltage distribution (top view);
    \item The epitaxy current distribution (top view);
    \item The substrate voltage distribution (side view from Y-axis);
    \item The substrate current distribution (side view from Y-axis);
    \item The per-layer normalized substrate voltage focusing (side view from Y-axis);
    \item The per-layer normalized substrate current focusing (side view from Y-axis);
\end{itemize}

    \subsection{\dwF integrated circuits under \bbi \ddcnew}
    \input{3_modeling/figures/modelesSimusResul/SimuResultDualWell.tex}
    Fig. \ref{fig_simuResDw} presents the six simulation results for a \dwF substrate integrated circuit.
    Sub-fig. \ref{subfig_vsupplyDw} shows us the power supply differential voltage distribution across the entire IC (top-view).
    As mentioned before, the power rails are located at the top and bottom of the IC.
    Quite naturally, we can observe less deviation from the nominal 1.2 V value at these spots.
    However, at the IC center, just below the probe, the power supply differential voltage rises up to 2.8 V.
    This represents a 133 \% increase over the nominal value.
    Fortunately, it lasts only a few dozen of nanoseconds.

    Sub-fig. \ref{subfig_iEpiDw} shows us the current distribution at the epitaxy level (the highest substrate layer), which represents the charges going from the substrate to the top of the \scs.
    What is worth noting here is that most of the charges are flowing through the center of the IC (a.k.a below the probe).
    It is to be expected with an isotropic environment such as the substrate.
    It is also natural to observe when comparing with sub-fig. \ref{subfig_vsupplyDw}, where the power delivery deviation were stronger below the probe.

    Sub-fig. \ref{subfig_vsubcDw} and \ref{subfig_isubcDw} respectively illustrate the voltage distribution and the current distribution respectively across the substrate from a cross-sectional view at the center of the IC along the Y-axis.
    These results are interesting as they show the homogeneous propagation of the energy through the substrate, with equipotentials forming half-circles.
    In addition to this, these results show a clear example of a DC-coupled probe with the IC.
    Indeed, the substrate acts as a voltage divider, and the further we are from the probe, the lower the voltage is.
    However, these results are not practical enough to fully appreciate the concentration of charges inside the substrate.
    To that end, and to better show these results, let us analyze sub-fig. \ref{subfig_vsubConc} and \ref{subfig_isubConc}.

    As for sub-fig. \ref{subfig_vsubcDw} and \ref{subfig_isubcDw}, they represent respectively the voltage concentration and the current concentration.
    For each substrate layer (14 layers in that case as we simulated a 140 µm substrate), the voltage was normalized along the 3D Y-axis, thus allowing to grasp and compare each layer to the other.
    The higher the layer number, the closer to the probe, and the lower the normalized value, the higher the charge concentration.
    What is very interesting to remark here is that on both sub-figures and for each layer, most charges are focused in the center of the layer.
    Then, the deeper we go inside the substrate, the wider the focusing.
    This result is to be expected.
    Indeed, because the charges diffuse homogeneously inside the substrate, the further they are from the probe, the more they have diffused.
    However, even in the deepest layer (layer 0), most of them are still highly focused below the probe.
    Therefore, it allows us to see that most of the energy is transferred directly under the probe.

%    Sub-fig. \ref{subfig_iEpiDw} shows the epitaxy voltage distribution (view from above the IC) at the apex of the disturbance.
%    This layer consists in the higher substrate layer, in other words the substrate layer the closest to the top of the \scs.
%    Each spot represents the current flowing through the substrate to the top of the \scs.
%    What is interesting to remark here is the locality of the injection.
%    Indeed, the current distribution is mostly channeled above the probe (a.k.a at the center of the IC).
%    Therefore, by cross-comparing the power supply voltage distribution shown in sub-fig. \ref{subfig_vsupplyDw} with the epitaxy voltage distribution, we can see that the power supply disturbance is stronger at the center of the IC.
%    With this in mind, we can say that the logic gates located above the probe are more prone to malfunctioning due to the higher amount of energy transferred to them, compared to the others.
%
%    Then, sub-fig. \ref{subfig_vsubcDw} and sub-fig. \ref{subfig_isubcDw} show the current and voltage distribution across the voltage (viewed from the side for more clarity).
%    As the substrate is an electrically isotropic environment, it is natural to observe such distribution, with high current and voltage close to the probe, which then spreads evenly all cross its volume to finally reach the logic gates.
%
%    Eventually, an important thing to remark here is that  the voltage distribution in the substrate indicates a DC-coupling between the probe and the IC.
%    Indeed, the substrate and the top of the \scs act as a big resistor divider, thus explaining the lower voltage the further from the probe.
%    It is important to note as it means that this is possible, for an attacker, to continue injecting energy into the IC during the pulse plateau, which would be impossible in a capacitive coupling scenario.
    \subsection{\twF integrated circuits under \bbi \ddcnew}
    \input{3_modeling/figures/modelesSimusResul/SimuResultTripleWell.tex}
    Fig. \ref{fig_simuResTw} presents the simulation results for a \twF substrate integrated circuit.
    Sub-fig. \ref{subfig_vsupplyTw} shows the power supply differential voltage distribution (top-view).
    As for the \dwF IC, the power rails are located at the top and bottom.
    What should be observed here is that there are less spatial variations compared to the \dwF substrate, and the power supply voltage is lower at the center of the IC instead of being higher.
    In addition to this, the deviation is a lot less important on that case, with a voltage only down to 1.1 V from the nominal 1.2 V.

    Sub-fig. \ref{subfig_iEpiTw} shows us some interesting results.
    At the peak of the disturbance, there is almost no current at the epitaxy level.
    At first glance, it can seem odd, but we will explain why this is logical thanks to the substrate distribution results which follow.

    Therefore, sub-fig. \ref{subfig_vsubcTw} and \ref{subfig_isubcTw} show the voltage and current distribution inside the substrate from a cross-sectional view.
    The results might seem similar to the ones of the \dwF substrate, but they are not.
    Indeed, when looking at the voltage and current scales, we can remark two things:
    \begin{itemize}
        \setlength\itemsep{-0.1em}
        \item The voltage distribution is extremely homogeneous, with an average value of -236 V;
        \item The current distribution is very low when compared to the \dwF substrate, with still a slight amount of current at the probe location.
    \end{itemize}
    These results are explained by the fact that with negative pulses in a \twF substrate, both silicon junction diodes are not conducting.
    Therefore, the \twF simulated IC acts as a big capacitor.
    The system probe/substrate is then AC-coupled to the top of the \scs.
    Then, similar to one side of a capacitor, the substrate charges up to the set-point value, if it has enough time to do so, or to a lower value (-236 V here) if it does not have enough time.
    Eventually, because only AC signals can pass through a capacitor, the current tends to be zero on the pulse plateau.

    Sub-fig. \ref{subfig_vsubConcTW} and \ref{subfig_isubConcTW} show, as before, the normalized current concentration for each substrate layer.
    Because the substrate network is identical in both simulated ICs, we observe the same result as before, with a strong concentration of charge below the probe, and a charge diffusion when going deeper into the substrate.
%    Sub-fig. \ref{subfig_iEpiTw} shows the epitaxy voltage distribution (view from above the IC) at the apex of the disturbance.
%    The first thing to remark when compared to the \dwF results is the very low current all across the epitaxy layer.
%    Then, when observing the power supply voltage distribution, shown in sub-fig. \ref{subfig_vsupplyTw}, there are less spatial variation compared to the \dwF substrate, and the power supply voltage is lower at the center of the IC instead of being higher.
%    In addition to this, the deviation is a lot less important on that case, with a voltage only down to 1.1 V from the nominal 1.2 V.
%    We can observe the same phenomenon on both substrate results (sub-fig. \ref{subfig_vsubcTw} and sub-fig. \ref{subfig_isubcTw}), where the current distribution shows a lower amount of current and the voltage distribution is almost uniform, as if the voltage stabilized itself during the pulse plateau.
%
%    It is explained thanks to the coupling existing between the probe and the top of the IC, which is, in that case, purely capacitive.
%    Therefore, it is impossible to continue injecting energy during the plateau, but only during pulse edges.
%    The circuits acts as a big capacitance, thus explaining the lower current at the apex of the disturbance and the voltage stabilization to the pulse plateau value, like it is observed in an electric capacitor.

    \subsection{Major differences between \dwF and \twF circuits}
    The main behavioral differences between \dwF and \twF substrate types lie in the substrate structure, more precisely in the way transistors are lithographed.
    Indeed, as I have stated previously, in \dwF substrates, NMOS are lithographed directly into the P-substrate, which allows a DC coupling between the backside of the IC and the NMOS.
    On the other hand, in \twF substrates, as NMOS and PMOS are electrically isolated from the substrate thanks to the P-well and the N-well.
    Therefore, no DC coupling is possible between neither the PMOS nor the NMOS.
    This is because silicon diodes are blocked, and thus act as capacitors.
    Therefore, the substrate is AC-coupled with the logic gates in a \twF substrate, while it is DC-coupled with the NMOS and AC-coupled with the PMOS in a \dwF substrate.
    These structural differences result in behavioral differences when performing \bbi, as we have observed thanks to the simulations.
    Therefore, it changes the way one can create faults in an IC, or an IC region, depending on the substrate type.
    In addition to this, because energy can only flow during voltage changes in an AC-coupled scenario, the effective current over a given injection with fixed parameters will always be lower on a \twF substrate compared to a \dwF substrate, where the DC-coupling allows for energy transfer during the pulse plateau.

    \subsection{\dwF and \twF circuits in practice \ddcnew}
    \input{3_modeling/figures/modelesSimusResul/cartoIgnd.tex}
    Thanks to the previous observations and conclusions, we can expect to observe such substrate structural differences on an actual IC.
    Therefore, we can expect \dwF regions to exhibit a higher amount of measured RMS current over \twF for a fixed set of experimental parameters.
    To that end, we chose to use our STM32F439 IC target and perform straightforward experiments.

    We called these experiments IC ground current mapping, and consists in choosing an arbitrary set of fixed pulse parameters, and performing a spatial sweep of the entire IC backside while measuring the current going out of the target ground connector at each location.
    For clarity purposes, only the RMS current is displayed in the mapping results.
    It is important to remark that in these experiments, the IC is powered-off, but connected to its main power supply.
    Fig. \ref{cartoIgnd} shows experimental results for a 50 µm thick IC, and Fig. \ref{photostm} shows an IR photograph of the exact same target for comparison purposes.
    The experimental parameters are the following:
    \begin{itemize}
        \setlength\itemsep{-0.1em}
        \item Voltage pulse amplitude: -70 V;
        \item Voltage pulse width: 20 ns;
    \end{itemize}
    When analyzing the results, we can notice strong differences in the measured RMS current between various areas.
    Therefore, we could suppose that the areas showing a bigger RMS current are composed of \dwF substrates, while the areas showing a lower current are composed of \twF substrates.
    It is indeed true.
    At the bottom-right are located the analog blocks, such as the voltage regulators and the PLLs.
    On the one hand, concerning our target technology, analog areas are typically manufactured using \dwF substrate.
    On the other hand, glue logic, such as the CPU core and the cryptographic coprocessor are manufactured using \twF substrates, to take advantage of the isolation it provides.
    As expected, the measured current above the glue logic is lower compared to the analog or the FLASH control area.

%\section{Voltage pulse generator model and further validation \ddcold}
%\label{section:genModel}
%
%Introducing the generator did not come without major problems.
%Indeed, the latter inevitably interacts with the target IC, and depending on the real generator output stage architecture, this interaction can drastically vary from one to another.
%
%For example, when using ESD guns as in \cite{japbbi, japbbi2}, their output stages are usually AC-coupled, while on our works, we mostly use DC-coupled generators.
%These subtle differences in practice become major issues in simulation when not treated correctly.
%Indeed, even considering the transmission line as it has been recommended in Chapter \ref{chap:2goodPractices}, most DC-coupled high voltage generators use a high-impedance mode to disconnect the load from the generator before and after the generated pulses.
%Therefore, one has to consider this specific aspect when designing a proper BBI electrical model, as we will explain in this section.
%
%\subsection{Early generator models \ddcold}
%\label{subsection:earlyGenModel}
%
%The first models consisted in a PWL voltage source directly connected to the substrate of the IC, and we quickly observed abnormal operating point values.
%\textcolor{orange}{Je dois rajouter des valeurs chiffrées.}
%Indeed, in this setup, at rest, the generator is equivalent a DC voltage source applying 0 V to the backside of the simulated IC.
%Therefore, it applies an undesired bias to the substrate and thus changes the operating point, inducing a high amount of charges flowing between power sources, thus disturbing the power delivery network.
%To circumvent this issue, we chose to mimic the behavior of an actual high voltage pulse generator and to switch between a high impedance mode and a voltage pulse mode as a function of the pulse time.
%This allowed to observe correct operating points with the generator connected, as it is the case in a real experiment.
%\textcolor{orange}{Je rajouterai les figures.}
%
%\subsection{Further generator models and verification \ddcold}
%\label{subsection:furtherGenModel}
%
%Because the previously explained generator model is electrically perfect and does not include any impedance mismatching effects, we extended the model to include the generator output impedance and the transmission line.
%\textcolor{orange}{Peut-être faire un schéma ?}
%It allowed us to observe impedance mismatch effects, which are of great importance when performing BBI (Chapter \ref{chap:1intro}), as the injected pulses are very fast and of high amplitude.
%Thus, impedance mismatch greatly changes the effective applied voltage pulse and injected currents, while also modifying unpredictably the induced disturbances, as we will observe further in this manuscript.
%
%\input{3_modeling/figures/simuCurrentMaps/coupeCourant.tex}
%In order to verify more thoroughly the soundness of the proposed models, a circuit under BBI is simulated in order to analyze the current distribution and amplitude, specifically at the peak of the voltage pulse.
%Fig. \ref{fig:coupeCourantDwTw} presents the results for both dual-well and triple-well ICs.
%The substrate being a resistive environment, it is natural to observe isotropic hemispheric current distributions.
%However, it is interesting to notice that the results show a lower amount of current concerning the triple-well IC compared to the dual-well one.
%It can be explained thanks to the coupling between the probe/substrate and the logic gates.
%On one hand, as shown in Fig. \ref{fig:dualTripleIvx}, in the dual-well IC, the charges do not have to cross any silicon junction in order to reach the NMOS transistors, while there is one junction between the probe and the PMOS transistors.
%On the other hand, concerning the triple-well IC, there is always at least one silicon junction to cross in order to reach the transistors.
%Because of this, and because the voltage pulse will inevitably bias the diode, it will change the coupling whether the diode is conducting or blocking.
%When the diode is conducting, the transistors are DC-coupled to the probe, whereas when the diode is blocking, the transistors are AC-coupled.
%In the second case, it means that charges can flow only on the edge of the pulse.
%Thus, during the pulse's plateau, there is no charge flow.
