
\section{Theoretical modeling: the effects of substrate thickness on \bbi \ddcpu}
\label{chap4:sect:geomModel}
%\input{4_thinning/figures/geomSubCurr}
In this section, I first present the geometric approach, allowing an abstraction from electronics, enabling faster and easier modeling at first.
Then, and because this modeling alone is insufficient, I perform and analyze electric IC simulations to strengthen the geometric approach conclusions.
%To begin with, we will address the geometric approach.
%It has been chosen thanks to the advantages it brings forward, such as the abstraction from electronics it enables, thus allowing easier and faster modeling.
%However, because this approach alone is insufficient, we will then study an analogous electrical one.

\subsection{Geometric modeling \ddcpu}
\label{chap4:sect:geomModel:subsect:geomModel}
\input{4_thinning/figures/geomCrossView}
For the purpose of the geometric modeling, let us consider two identical ICs.
A commercial one, with an arbitrary standard substrate thickness, and another one with its substrate thinned by a certain amount in order to perform fault injection more easily.
Fig. \ref{fig:geomCrossView} illustrates the two-dimensional cross-sectional views of the considered ICs substrates during an arbitrary BBI voltage pulse of amplitude $V_{P_U}$.
The probe is located at the center of the ICs at point $P_U$, and the targeted spot in the SCS layer (logic gates) is at point $P$.
The silicon substrate being an isotropic resistive environment, it is quite natural to expect the electrical charges to flow and spread evenly when injected into it at any given time.
Therefore, equipotentials form half-sphere surfaces inside the substrate volume.
These surfaces are highlighted in two-dimensions as green half-circles in Fig. \ref{fig:geomCrossView}, for an arbitrary voltage $V_F$.

In this scenario, an attacker wants to induce a fault in the logic gates, located at the top of each IC.
To that end, they need to change the voltage enough at point $P$, called $V_P$, in order to disturb the transistors and change the logic gates behavior for a short amount of time.
In addition to that, and for the sake of simplicity, let us assume that $P$ is the only location in the considered IC where faults can be injected.
However, in order to observe faults at point $P$, $V_P$ needs to reach a minimal threshold voltage, called $V_F$.
Because the attacker is working with BBI, a metallic probe is connected onto the backside of the IC, at point $P_U$, in order to inject energy into the IC.
Depending on the amount of injected energy, in other words, the maximum amplitude of the voltage pulse because the substrate effective electric resistance is static over time, the voltage at $P$ might never reach $V_F$, therefore, no faults will be observed.
Let us consider that the attacker chose an amplitude $V_{PU}$ big enough such that at a given moment in the injection, $V_P$ reaches $V_F$ or more in each considered IC.
In that scenario, the area on the IC front side where $V > V_F$ is a disk of radius $\phi$, centered in $P$, called the BBI susceptibility area radius.
It means that the attacker can position the probe anywhere on the backside within this disk to reach $V_F$ at $P$, and therefore induce a fault at $P$.

Let me introduce the various equations enabling the calculation of the various parameters I previously mentioned.
The half-sphere equipotential radius relative to time can be determined thanks to the following formula:
\begin{equation}
    r(t) = \frac{\rho_{SUB}}{\sqrt{2}} \cdot \frac{|I_G(t)|}{|V_{PU}(t) + V_F|}
\end{equation}
with $\rho_{SUB}$ the resistivity of the silicon substrate, $I_G(t)$ the instantaneous sum of the current distribution contained in the half-sphere, and $V_{PU}(t)$ the instantaneous voltage pulse applied on the backside of the IC.

Then, logically, the BBI susceptibility area radius, denoted $\phi_r$, is given by:
\begin{equation}
    \phi_r(t) = 2 \cdot \sqrt{r(t)^2 - t^2_{SUB}}
\end{equation}
with $t_{SUB}$ being the IC substrate thickness.

As illustrated in Fig. \ref{fig:geomCrossView}, thinning the substrate inevitably increases the size of the susceptibility area if the experimental conditions are constant.
It means that the susceptibility evolution ratio is always greater than 1 when thinning the substrate for a fixed disturbance:
\begin{equation}
    \frac{\phi_r^{THIN}}{\phi_r^{THICK}} = \sqrt{\frac{r^2 - t^2_{THIN}}{r^2 - t^2_{THICK}}} > 1
\end{equation}

Therefore, in order to obtain the same susceptibility area with a thinner IC, it is required to reduce the voltage pulse amplitude, thanks to the following relation:
\begin{equation}
    \label{chap4:sect:geomModel:eqnVpu*}
    V_{PU}^* = \frac{t_{THIN}}{t_{THICK}} \cdot V_{PU} + V_F \cdot (1 - \frac{t_{THIN}}{t_{THICK}})
\end{equation}

Eventually, this geometric approach allows deducing three related outcomes:
\begin{enumerate}
    \setlength\itemsep{-0.1em}
    \item Thinning the substrate allows reducing the minimal voltage pulse amplitude required to induce a fault while keeping a constant susceptibility area.
    \item The BBI susceptibility area increases while the substrate thickness decreases while working at a constant voltage pulse $V_{PU}$.
    \item Thinning the substrate alone does not have an influence on BBI spatial resolution, as the susceptibility area depends on the couple $(t_{SUB}, V_{PU})$. Thus, similar spatial resolution could be obtained with different substrate thicknesses by changing $V_{PU}$.
\end{enumerate}

%\newpage
\subsection{Electric approach \ddcpu}
\label{chap4:sect:geomModel:subsect:elecApproach}
%\input{4_thinning/figures/simuSubCoupe}
\input{4_thinning/figures/simuSubCoupe2}
As I stated previously, in order to verify the meaningfulness of the geometrical approach, I complete it with an electrical modeling approach.
This approach takes advantage of the models I previously introduced in chapter \ref{chap:3icModeling}.
Then, thanks to these models, I am able to generate identical ICs with different substrate thicknesses.
After that, I simulate the circuits under \bbi and I am able to plot the voltage distribution inside the substrate for each simulated IC.
%For this purpose, I reused the models I previously introduced in Chapter \ref{chap:3icModeling}.
%The electrical approach consists in generating identical ICs with different substrate thicknesses and simulating them during BBI.
%The considered ICs are 550 µm wide and 450 µm deep, similar to Chapter \ref{chap:3icModeling}.
%It consists in utilizing the models presented in Chapter \ref{chap:3icModeling} with different substrate thicknesses.
%To that end, the same IC will be used, with an 550 µm width and an 450 µm depth.

I chose to study two distinct substrate thicknesses: 60 µm and 140 µm.
The simulation parameters are the following:
\begin{itemize}
    \setlength\itemsep{-0.1em}
    \item \dwF exclusive substrate
    \item Required voltage pulse: -300 V
    \item Required pulse width: 20 ns
    \item Required rise and fall times: 8 ns
\end{itemize}

Fig. \ref{figSimuSubCoupe2} shows, for each simulated IC, the voltage distribution across the substrate through a cross-sectional view at the apex of the voltage pulse first edge, in addition to the per-layer voltage density.
These last graphs allow me to spot more easily the way the voltage propagates and is distributed inside the substrate during \bbi.
For simplicity, the results are shown in two dimensions, and as the substrate is an isotropic environment, the propagation is uniform in every direction.

The first interesting thing to note is that, as predicted thanks to the geometric model and as shown in Fig. \ref{subFigThickIC} and \ref{subFigThinIC}, equipotentials effectively form half-circles into the substrate (which are effectively half-spheres in 3D).
However, these figures alone do not say much, at least not very obviously, about the voltage spreading inside the substrate.
Then, thanks to Fig. \ref{subFigThickICfocus} and \ref{subFigThinICfocus}, which represent, for each substrate layer (14 in number concerning the 140 µm IC, 6 for the 60 µm IC), the normalized voltage distribution.
The lower the layer number (or the closer to the red color the line is), the deeper into the IC it is.
Concerning the values in the X-axis, there are normalized voltage values calculated per-layer, and the closer to zero, the higher the density.
What these figures show us is that for identical experimental parameters, when the substrate is thinned, the voltage density is higher in the highest substrate layer.
It means that for a fixed $V_F$ voltage threshold, the \bbi susceptibility area is more spread out on a thinner IC.
It is quite intuitive when looking at the simulation results.
Indeed, if I simply remove the additional layers in Fig. \ref{subFigThickIC} and \ref{subFigThinIC} between the 60 µm and the 140 µm IC, the results look very similar.
The same observation can be made concerning Fig. \ref{subFigThickICfocus} and \ref{subFigThinICfocus}.
%I annotated two equipotentials according to their voltage and annotated their size in Fig. \ref{figSimuSubCoupe2}.
%As one can see, the yellow half-circle (-140 V, 40 µm), formed close to the probe, is complete in each considered IC.
%However, similar to the geometric modeling, the blue half-circle (-28 V,  140 µm), is entirely included into the 140 µm IC (Fig. \ref{subFigThickIC}), while it is cut at the epitaxy level in the 60 µm IC.
